Choreography settings: 
***********************

2017_02_12
java -XX:-DoEscapeAnalysis -Xmx6G -cp /Users/katiepodshivalova/Documents/Kenyon_Lab/Tracking_healthspan/Choreography/Chore.jar:/Users/katiepodshivalova/Documents/Kenyon_Lab/Tracking_healthspan/Choreography/scala-library.jar:/Users/katiepodshivalova/Documents/Kenyon_Lab/Tracking_healthspan/Choreography/IchiMwt.jar:/Users/katiepodshivalova/Documents/Kenyon_Lab/Tracking_healthspan/Choreography/jtransforms-2.4.jar:/Users/katiepodshivalova/Documents/Kenyon_Lab/Tracking_healthspan/Choreography/commons-math3-3.1.1.jar:/Users/katiepodshivalova/Documents/Kenyon_Lab/Tracking_healthspan/Choreography/Dejitter.jar Choreography -p 0.02577 -M 1 -t 30 --shadowless -S --plugin Dejitter --plugin Reoutline::exp --plugin Respine --plugin SpinesForward --plugin MultiSensed::report=bfnos -o number,goodnumber,persistence,length,width,midline,aspect,curve,speed,bias --target /Users/katiepodshivalova/Documents/Kenyon_Lab/KPCA021_Track_wo_FUDR/KPCA021_Choreography_out/Dejitter /Users/katiepodshivalova/Documents/Kenyon_Lab/KPCA021_Track_wo_FUDR/KPCA021_MWT_raw_data/TrackerA/Completed/$D

1) Create a dataframe with all of the data:
```{r}
# List files:
setwd("/Users/katiepodshivalova/Documents/Kenyon_Lab/KPCA021_Track_wo_FUDR/KPCA021_Choreography_out/Dejitter") # this is the dir that contains all of your .dat files
file_list <- list.files(pattern = "\\.dat$")
file_list <- file_list[file.info(file_list)$size!=0]

# Write a function that will combine all the .dat files into a single dataframe
# Each variable will be a factor and will be listed in its own column
# For example my variables were: strain, FUDR, sample number, and tracker color
# So, I added 5 extra columns to each file
# You'll have to adjust this piece of code according to how many variables you have
compile_data <- function(file_list){
        dataset <- data.frame()
        day_col <- vector()
        strain_col <- vector()
        FUDR_col <- vector()
        sample_col <- vector()
        tracker_col <- vector()

        for (file in file_list){
                day <- (strsplit(file, "_")[[1]])[1] # day is the first entry in a file name delimited by "_"
                day <- gsub("^.{1}","", day) # remove the "d" in fron of "d1", "d2", etc.
                day <- as.numeric(day) # convert day from character to numeric
                strain <- (strsplit(file, "_")[[1]])[2] # strain is the second entry in a file name delimited by "_"
                FUDR <- (strsplit(file, "_")[[1]])[3] # FUDR is the third entry in a file name delimited by "_"
                sample <- (strsplit(file, "_")[[1]])[4] # sample number is the fourth entry in a file name delimited by "_"
                tracker <- (strsplit(file, "_")[[1]])[5] # tracker color is the fifth entry in a file name delimited by "_"
                
                temp_dataset <- read.table(file, header=FALSE) # read each file in the list of files
                day_col <- c(day_col, rep(day,length(temp_dataset[,1]))) # create a column that corresponds to the day
                strain_col <- c(strain_col, rep(strain,length(temp_dataset[,1]))) # same but for strain, FUDR, etc...
                FUDR_col <- c(FUDR_col, rep(FUDR,length(temp_dataset[,1])))
                sample_col <- c(sample_col, rep(sample,length(temp_dataset[,1]) ))
                tracker_col <- c(tracker_col, rep(tracker,length(temp_dataset[,1]) ))
                dataset <- rbind(dataset, temp_dataset) # add the results from each file to the growing dataframe
                rm(temp_dataset)   
        }
        dataset <- cbind(dataset, day_col, strain_col, FUDR_col, sample_col, tracker_col) # combine your dataframe with the extra columns you created
        
        
        # Give column names to your dataframe
        # This is where it's important to remember the order in which you output different parameters using choreography
        # Also create names for the new columns you created
        colnames(dataset) <- c("Time", "Number", "Goodnumber","Persistence","Length","Width","Midline","Aspect","Curve","Speed","Bias","Day","Strain","FUDR", "PlateNum", "Tracker")
        dataset$Day <- factor(dataset$Day)
        print(dataset)
  
}

# Run the function you've just created
# Save output to a new object called "dataset"
dataset <- compile_data(file_list)
dataset$Tracker <- sub(".dat","", dataset$Tracker) # remove the .dat
# If you have any typos, fix them like this:
levels(dataset$FUDR)[levels(dataset$FUDR)=="wth"] <- "with"
# Convert tracker to a factor
dataset$Tracker <- factor(dataset$Tracker)

# Save your dataset for future use
save(dataset,file="KPCA021_dat_dataset_dejitter.Rda")
# You can load it like this next time:
load("/Users/katiepodshivalova/Documents/Kenyon_Lab/KPCA021_Track_wo_FUDR/MeanAnalysis/Dejitter/KPCA021_dat_dataset_dejitter.Rda")
```

2.1) Plot a parameter of all conditions over the course of tracking:
```{r}
library(ggplot2)

dataset1 <- dataset[dataset$Strain == "e1370",]
ggplot()+
        geom_point(data=dataset1, aes(x = Time, y = Speed, color=Tracker), alpha=0.8, size=0.02)+
        #ggtitle("N2E") +
        #scale_color_manual(values=c("orange","blue","red"),labels=c("backward", "forward", "omega"))+
        xlab("Time (s)")+
        ylab("Mean speed")+
        #theme(panel.margin = unit(1, "lines"))+
        #theme(axis.text=element_text(size=3), axis.title=element_text(size=3,face="bold"), strip.text=element_text(size=3))+
        #coord_cartesian(ylim=c(0,0.4))
        theme_bw()+
        theme(axis.line = element_line(colour = "black"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank(),
          axis.text = element_text(size = 8))+
        facet_grid(Day ~ FUDR, labeller=label_both)
        # scale_x_continuous(breaks=seq(0,1260,300))
ggsave("Speed_over_Time_e1370.png", width=12, height=10)
```

2.2) Plot a parameter of 1 condition over the course of tracking 
```{r}
dataset2 <- dataset[dataset$Strain == "N2E",]
dataset2 <- dataset2[dataset2$FUDR=="with",]
dataset2 <- dataset2[dataset2$Day=="16",]

ggplot()+
  geom_point(data=dataset2, aes(x=Time, y=Speed, color=PlateNum), size=0.001)+
  xlab("Time (s)")+
  ylab("Mean speed (mm/s)")+
  scale_x_continuous(breaks=seq(0,960,50))+
  theme_bw()+
  theme(
          axis.line = element_line(colour = "black"),
          # panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          # panel.border = element_blank(),
          panel.background = element_blank(),
          axis.text = element_text(size = 10))
# ggsave("Speed_d13_N2E_withoutFUDR_over_Time.png", width=12, height=10)  
```


3) Plot disbributions (box and whiskers plot OR dot plots) of a feature for each day:
```{r}
subset <- dataset[dataset$Time>700&dataset$Time<890,]

library(plyr)
subset <- ddply(subset, .(Strain, FUDR, Day), function(d){ 
                Q1=quantile(d[,"Speed"], 1/4, na.rm=TRUE)
                Q3=quantile(d[,"Speed"], 3/4, na.rm=TRUE)
                IQR=Q3-Q1
                upper.limit=Q3+1.5*IQR
                lower.limit=Q1-1.5*IQR
                d[(d[,"Speed"] - lower.limit)*(upper.limit - d[,"Speed"]) > 0,]
        })

subset <- subset[subset$Day=="1" | subset$Day=="2"| subset$Day=="3"| subset$Day=="5"| subset$Day=="7"| subset$Day=="9",]
# Some speeds are 0 (tracker didn't work; remove these)
# hist(subset[subset$Strain=="N2E"&subset$Day=="2"&subset$FUDR=="with"&subset$Tracker=="A","Speed"])
subset <- subset[subset$Speed != 0,]

library(ggplot2)
    ggplot()+
    geom_boxplot(data=subset, aes(x=Strain, y=Speed, color=Strain), size=0.3, outlier.shape = NA)+
    # geom_jitter(data=subset, aes(x=FUDR, y=Speed, color=FUDR),position = position_jitter(width = 0.6), alpha=0.5)+
    scale_y_continuous(limits=c(0, 0.24))+
    xlab("Days")+
    ylab(" Mean speed (mm/s) \n")+
    ggtitle("700 - 800 s \n")+
    scale_fill_manual(name="Strain",
                          breaks=c("N2E","e1368","e1370"),
                          labels=c("N2","daf-2(e1368)","daf-2(e1370)"),
                          values=c('black','green3','magenta'))+
     scale_color_manual(name="Strain",
                          breaks=c("N2E","e1368","e1370"),
                          labels=c("N2","daf-2(e1368)","daf-2(e1370)"),
                          values=c('black','green3','magenta'))+
    theme_bw()+
    theme(axis.text.x = element_blank(),
          axis.ticks=element_blank(),
          text = element_text(size=12),
          axis.text = element_text(color="black"),
          legend.key = element_rect(fill = "white"))+
       facet_grid(FUDR~Day)
    # ggsave("Boxplots_Speed_900-901_s_by_Strain.pdf", width =20, height = 15, dpi=300)
    # ggsave("Boxplots_Speed_700-890_s_by_FUDR_d1-9.pdf", width =20, height = 10, dpi=300)
rm(subset)
```

4.1) Calculate feature means and sd/s.e.m. for each day:
```{r}
# Define a function and then run the function using the parameters of your choosing
feature_means <- function(start=0, end=1260, feature="Speed", variance="se", norm="self"){
        time_interval <- dataset[dataset[,"Time"]>start&dataset[,"Time"]<end,]
        
  # Remove feature outliers using: [Q1 - 1.5 * IQR, Q3 + 1.5 * IQR] b/c some data isn't normal:          
        library(plyr)
        rm_outliers <- ddply(time_interval, .(Strain, FUDR, Day), function(d){ 
                Q1=quantile(d[,feature], 1/4, na.rm=TRUE)
                Q3=quantile(d[,feature], 3/4, na.rm=TRUE)
                IQR=Q3-Q1
                upper.limit=Q3+1.5*IQR
                lower.limit=Q1-1.5*IQR
                d[(d[,feature] - lower.limit)*(upper.limit - d[,feature]) > 0,]
        })
        
# Calculate feature means and variance:
  # If want SD:
        if (variance=="sd"){
          chron_feature <- ddply(rm_outliers, .(Strain, FUDR, Day),function(d){
              mean = mean(d[,feature],na.rm=TRUE)
              sd = sd(d[,feature], na.rm=TRUE)
              c(mean,sd)
              })
          colnames(chron_feature) <- c("Strain","FUDR","Day","mean","sd")
        }
  # If want SE:       
        if (variance=="se"){
          chron_feature <- ddply(rm_outliers, .(Strain, FUDR, Day),function(d){
              mean = mean(d[,feature],na.rm=TRUE)
              se=sd(d[,feature], na.rm=TRUE)/sqrt(mean(d[,"Goodnumber"]))
              N = mean(d[,"Goodnumber"])
              c(mean,se,N)
            })  
          colnames(chron_feature) <- c("Strain","FUDR","Day","mean","se","N")
        }
        
  # Re-format and save feature means and variance dataframe:    
        chron_feature$Day <- as.numeric(levels(chron_feature$Day))[chron_feature$Day]
        chron_feature <- chron_feature[complete.cases(chron_feature),] #remove NAs
        chron_feature$Day <- chron_feature$Day-1 # Set Day 1 as Day 0 
        chron_feature$Strain <- factor(chron_feature$Strain, levels=c("N2E", "e1368", "e1370"))
        chron_feature$FUDR <- factor(chron_feature$FUDR, levels=c("with", "without"))
        do.call("<<-",list(paste(c(feature, "_", start,"_",end,"_s"), collapse=""), chron_feature))
        
        
  # Normalize feature to day 1 (day 2 if start counting from 0):
        daily_mean <- ddply(rm_outliers, .(Strain, FUDR, Day),function(d){
            d1_mean=mean(d[,feature], na.rm=TRUE)
            })
        colnames(daily_mean) <- c("Strain","FUDR","Day","d1_mean")
        
  # If want to normalize to d1 of each Strain:FUDR combination:
      if (norm=="self"){
        daily_mean <- daily_mean[daily_mean$Day==1,]
        daily_mean <- subset(daily_mean, select = -Day)
        rm_outliers <- merge(rm_outliers, daily_mean, by=c("Strain","FUDR"))
        rm_outliers$norm_to_d1 <- rm_outliers[,feature]/rm_outliers[,"d1_mean"]        
      }
  # If want to normalize all features to N2E with FUDR on d1:
      else {
        daily_mean <- daily_mean[daily_mean$Day==1&daily_mean$Strain=="N2E"&daily_mean$FUDR=="with",] 
        rm_outliers$norm_to_d1 <- rm_outliers[,feature]/daily_mean[,"d1_mean"]
      }
  # If want SD:
        if (variance=="sd"){
          chron_feature_norm_d1 <- ddply(rm_outliers, .(Strain, FUDR, Day), summarise, mean = mean(norm_to_d1,na.rm=TRUE), sd = sd(norm_to_d1, na.rm=TRUE))
        }
  # if want SE:
        if (variance=="se"){
          chron_feature_norm_d1 <- ddply(rm_outliers, .(Strain, FUDR, Day), summarise, mean = mean(norm_to_d1,na.rm=TRUE), se=sd(norm_to_d1, na.rm=TRUE)/sqrt(mean(Goodnumber)), N = mean(Goodnumber))
        }
  # Re-format and save feature means and variance dataframe:        
        chron_feature_norm_d1$Day <- as.numeric(levels(chron_feature_norm_d1$Day))[chron_feature_norm_d1$Day]
        chron_feature_norm_d1 <- chron_feature_norm_d1[complete.cases(chron_feature_norm_d1),] #remove NAs
        chron_feature_norm_d1$Day <-  chron_feature_norm_d1$Day-1 # Set Day 1 as Day 0 
        chron_feature_norm_d1$Strain <- factor(chron_feature_norm_d1$Strain, levels=c("N2E", "e1368", "e1370"))
        chron_feature_norm_d1$FUDR <- factor(chron_feature_norm_d1$FUDR, levels=c("with", "without"))
        do.call("<<-",list(paste(c(feature,"_",start,"_",end,"_s","_norm_to_d1"), collapse=""), chron_feature_norm_d1))

        #Save as an excel spreadsheet
        # library(xlsx)
        # out_file_name <- paste(c(feature,"_",start,"_",end,".txt"), collapse="")
        # write.table(chron_feature, out_file_name, sep="\t")
        
}
# save(Speed_700_890_s, file="Speed_700_890_s_sem.Rda")
# save(Goodnumber_700_890_s, file="Goodnumber_700_890_s_sem.Rda")
```

4.2) Calculate feature means and sd/s.e.m.for EACH REPLICATE SEPARATELY for each day:
(this is super optional, but keeping it here just in case)
```{r}
feature_means_per_rep <- function(start=0, end=1260,feature="Speed",variance="sd",norm="self"){
        time_interval <- dataset[dataset[,"Time"]>start&dataset[,"Time"]<end,]
        
  # Remove feature outliers using: [Q1 - 1.5 * IQR, Q3 + 1.5 * IQR] b/c some data isn't normal:          
        library(plyr)
        rm_outliers <- ddply(time_interval, .(Strain, FUDR, Day), function(d){ 
                Q1=quantile(d[,feature], 1/4, na.rm=TRUE)
                Q3=quantile(d[,feature], 3/4, na.rm=TRUE)
                IQR=Q3-Q1
                upper.limit=Q3+1.5*IQR
                lower.limit=Q1-1.5*IQR
                d[(d[,feature] - lower.limit)*(upper.limit - d[,feature]) > 0,]
        })
        
# Calculate feature means and variance:
  # If want SD:
        if (variance=="sd"){
          chron_feature <- ddply(rm_outliers, .(Strain,FUDR,Day,PlateNum),function(d){
              mean = mean(d[,feature],na.rm=TRUE)
              sd = sd(d[,feature], na.rm=TRUE)
              c(mean,sd)
              })
          colnames(chron_feature) <- c("Strain","FUDR","Day","PlateNum","mean","sd")
        }
  # If want SE:       
        if (variance=="se"){
          chron_feature <- ddply(rm_outliers, .(Strain,FUDR,Day,PlateNum),function(d){
              mean = mean(d[,feature],na.rm=TRUE)
              se=sd(d[,feature], na.rm=TRUE)/sqrt(mean(d[,"Goodnumber"]))
              N = mean(d[,"Goodnumber"])
              c(mean,se,N)
            })  
          colnames(chron_feature) <- c("Strain","FUDR","Day","PlateNum","mean","se","N")
        }
  # Re-format and save feature means and variance dataframe:    
        chron_feature$Day <- as.numeric(levels(chron_feature$Day))[chron_feature$Day]
        chron_feature <- chron_feature[complete.cases(chron_feature),] #remove NAs
        chron_feature$Day <- chron_feature$Day-1 # Set Day 1 as Day 0 
        chron_feature$Strain <- factor(chron_feature$Strain, levels=c("N2E", "e1368", "e1370"))
        chron_feature$FUDR <- factor(chron_feature$FUDR, levels=c("with", "without"))
        do.call("<<-",list(paste(c(feature, "_", start,"_",end,"_s","_per_Plate"), collapse=""), chron_feature))
        
        
  # Normalize feature to day 1 (day 2 if start counting from 0):
        daily_mean <- ddply(rm_outliers, .(Strain,FUDR,Day,PlateNum),function(d){
            d1_mean=mean(d[,feature], na.rm=TRUE)
            })
        colnames(daily_mean) <- c("Strain","FUDR","Day","PlateNum","d1_mean")
  # If want to normalize to d1 of each Strain:Bacteria combination:
      if (norm=="self"){
        daily_mean <- daily_mean[daily_mean$Day==1,]
        daily_mean <- subset(daily_mean, select = -Day)
        rm_outliers <- merge(rm_outliers, daily_mean, by=c("Strain","FUDR","PlateNum"))
        rm_outliers$norm_to_d1 <- rm_outliers[,feature]/rm_outliers[,"d1_mean"]        
      }
  # If want to normalize all features to N2E on FUDR d1:
      else {
        daily_mean <- daily_mean[daily_mean$Day==1&daily_mean$Strain=="N2E"&daily_mean$FUDR=="with",] 
        rm_outliers$norm_to_d1 <- rm_outliers[,feature]/daily_mean[,"d1_mean"]
      }
  # If want SD:
        if (variance=="sd"){
          chron_feature_norm_d1 <- ddply(rm_outliers, .(Strain, FUDR, Day, PlateNum), summarise, mean = mean(norm_to_d1,na.rm=TRUE), sd = sd(norm_to_d1, na.rm=TRUE))
        }
  # if want SE:
        if (variance=="se"){
          chron_feature_norm_d1 <- ddply(rm_outliers, .(Strain, FUDR, Day, PlateNum), summarise, mean = mean(norm_to_d1,na.rm=TRUE), se=sd(norm_to_d1, na.rm=TRUE)/sqrt(mean(Goodnumber)), N = mean(Goodnumber))
        }
  # Re-format and save feature means and variance dataframe:        
        chron_feature_norm_d1$Day <- as.numeric(levels(chron_feature_norm_d1$Day))[chron_feature_norm_d1$Day]
        chron_feature_norm_d1 <- chron_feature_norm_d1[complete.cases(chron_feature_norm_d1),] #remove NAs
        chron_feature_norm_d1$Day <-  chron_feature_norm_d1$Day-1 # Set Day 1 as Day 0 
        chron_feature_norm_d1$Strain <- factor(chron_feature_norm_d1$Strain, levels=c("N2E", "e1368", "e1370"))
        chron_feature_norm_d1$FUDR <- factor(chron_feature_norm_d1$FUDR, levels=c("with", "without"))
        do.call("<<-",list(paste(c(feature,"_",start,"_",end,"_s","_norm_to_d1","_per_Plate"), collapse=""), chron_feature_norm_d1))
}
# save(Speed_700_890_s_per_Plate, file="Speed_700_890_s_per_Plate_sem.Rda")
save(Goodnumber_700_890_s_per_Plate, file="Goodnumber_700_890_s_per_Plate_sem.Rda")
```

5) Calculate -FUDR/+FUDR ratio for each day:
You can compare any two conditions this way (e.g. MUTANT/CONTROL)
```{r}
# Calculate
feature_means_FUDR_norm <- function(start=0, end=1260,feature="Speed",variance="se"){
      time_interval <- dataset[dataset[,"Time"]>start&dataset[,"Time"]<end,]
      # Remove feature outliers using: [Q1 - 1.5 * IQR, Q3 + 1.5 * IQR]:          
            library(plyr)
            rm_outliers <- ddply(time_interval, .(Strain, FUDR, Day), function(d){ 
                    Q1=quantile(d[,feature], 1/4, na.rm=TRUE)
                    Q3=quantile(d[,feature], 3/4, na.rm=TRUE) #This was originally incorrectly set to 2/4, fixed 4/28/15
                    IQR=Q3-Q1
                    upper.limit=Q3+1.5*IQR
                    lower.limit=Q1-1.5*IQR
                    d[(d[,feature] - lower.limit)*(upper.limit - d[,feature]) > 0,]
            })
            
      # Normalize feature to N2E:
            daily_mean <- ddply(rm_outliers, .(Strain, FUDR, Day),function(d){
                d <- d[d[,feature]!=0,]
                daily_mean=mean(log(d[,feature],2), na.rm=TRUE)
                })
            colnames(daily_mean) <- c("Strain","FUDR","Day","daily_mean")
        
            daily_mean <- daily_mean[daily_mean$FUDR=="with",]
            daily_mean <- subset(daily_mean, select = -FUDR)
            rm_outliers <- merge(rm_outliers, daily_mean, by=c("Day","Strain"))
            rm_outliers$Log2_norm_to_wFUDR <- log(rm_outliers[,feature],2) - rm_outliers[,"daily_mean"]        
            
            rm_outliers <- rm_outliers[rm_outliers$Log2_norm_to_wFUDR!=-Inf,]
            
      # If want SD:
            if (variance=="sd"){
              chron_feature_norm <- ddply(rm_outliers, .(Strain, FUDR, Day), summarise, mean = mean(Log2_norm_to_wFUDR,na.rm=TRUE), sd = sd(Log2_norm_to_wFUDR, na.rm=TRUE))
            }
      # if want SE:
            if (variance=="se"){
              chron_feature_norm <- ddply(rm_outliers, .(Strain, FUDR, Day), summarise, mean = mean(Log2_norm_to_wFUDR,na.rm=TRUE), se=sd(Log2_norm_to_wFUDR, na.rm=TRUE)/sqrt(mean(Goodnumber)), N = mean(Goodnumber))
            }
      # Re-format and save feature means and variance dataframe:        
            chron_feature_norm$Day <- as.numeric(levels(chron_feature_norm$Day))[chron_feature_norm$Day]
            chron_feature_norm <- chron_feature_norm[complete.cases(chron_feature_norm),] #remove NAs
            chron_feature_norm$Day <-  chron_feature_norm$Day-1 # Set Day 1 as Day 0 
            chron_feature_norm$Strain <- factor(chron_feature_norm$Strain, levels=c("N2E", "e1368", "e1370"))
            chron_feature_norm$FUDR <- factor(chron_feature_norm$FUDR, levels=c("with", "without"))
            do.call("<<-",list(paste(c(feature,"_",start,"_",end,"_s","_norm_to_wFUDR"), collapse=""), chron_feature_norm))
    
            #Save as an excel spreadsheet
            # library(xlsx)
            # out_file_name <- paste(c(feature,"_",start,"_",end,".txt"), collapse="")
            # write.table(chron_feature, out_file_name, sep="\t")
}
```

6.1) Plot features as a function of age:
```{r}
chronological_plot <- function (feature_table){
      plotting_data <- feature_table

      if (ncol(feature_table)==6){
        colnames(plotting_data) <- c("Strain","FUDR","Day","mean","variance","N")
      }
      if (ncol(feature_table)==5){
        colnames(plotting_data) <- c("Strain","FUDR","Day","mean","variance")
      }
      library(ggplot2)
      require(grDevices)  
      # Create a plot title
      start <- strsplit(deparse(substitute(feature_table)),"_")[[1]][2]
      end  <- strsplit(deparse(substitute(feature_table)),"_")[[1]][3] 
      feature <- strsplit(deparse(substitute(feature_table)),"_")[[1]][1] 
      title <- paste(c(feature, start, "-", end, "s"), collapse=" ")
      # Make the plot
      g <- ggplot(data=plotting_data, aes(x = Day, y =mean, color=Strain))  
      if (grepl("d1",deparse(substitute(feature_table)))){
              g + 
                geom_errorbar(data=plotting_data, aes(x=Day, y=mean, ymin=mean-variance, ymax=mean+variance, width=0.5)) + 
                geom_smooth(stat="identity", aes(linetype=FUDR)) + 
                geom_point(size=2) + 
                scale_color_manual(name='', values=c('black','green3','magenta'),labels = c('N2E','daf-2(e1368)','daf-2(e1370)'))+
                scale_linetype_manual(name='', values=c('solid','dotted'),labels = c('+ FUDR','-FUDR'))+
                ggtitle(title) +
                xlab("Days of adulthood") + 
                ylab(paste(c("Mean", strsplit(deparse(substitute(feature_table)),"_")[[1]][1]," +/- ", colnames(feature_table)[5],"", "vs. day 1"), collapse=" "))+
                theme(
                        legend.position = "bottom", 
                        axis.text = element_text(size = 10))
      }  
      else {
             g + 
                geom_errorbar(data=plotting_data, aes(x=Day, y=mean, ymin=mean-variance, ymax=mean+variance, width=0.6),size=0.4) + 
                geom_smooth(stat="identity", aes(linetype=FUDR), size=0.65) + 
                geom_point(size=1.5) + 
                scale_color_manual(name='', values=c('black','green3','magenta'),labels = c('N2E','daf-2(e1368)','daf-2(e1370)'))+
                scale_linetype_manual(name='', values=c('solid','dotted'),labels = c('+ FUDR','-FUDR'))+
                # scale_x_continuous(limits=c(-0.5,10.5))+
                ggtitle(title) + 
                xlab("Days of adulthood") +       
                ylab(paste(c("Mean",strsplit(deparse(substitute(feature_table)),"_")[[1]][1]," +/- ", colnames(feature_table)[5]), collapse=" "))+
                # scale_y_continuous(limits=c(0,0.2))
                theme(
                        legend.position = "bottom", 
                        axis.text = element_text(size = 10))
      }
        title <- paste(c(deparse(substitute(feature_table)),"_",".pdf"), collapse="")
        ggsave(title, width=4, height=5, dpi=600)
}        
```

7) Plot bar graph showing mean speed on a given day:
```{r}
bar_data <- Speed_700_880_s[Speed_700_880_s$Day==1|Speed_700_880_s$Day==2,]

ggplot(data=bar_data, aes(x=Strain, y=mean, fill=Strain))+
    geom_bar(stat="identity",position=position_dodge(width=0.9)) +  
    geom_errorbar(data=bar_data, aes(x=Strain, y=mean, ymin=mean-se, ymax=mean+se, width=0.5),position=position_dodge(width=0.9)) + 
    ggtitle("700-890s")+
    xlab("Day") +
    ylab("Unstimulated speed (mm/s) +/- s.e.\n") + 
    scale_fill_manual(values=c("black","green3","magenta"))+
    # scale_y_continuous(limits=c(0,0.115), breaks=seq(0,0.115,0.025))+
    theme_bw()+
        theme(
            legend.position = "bottom", 
            panel.grid.major = element_line(colour = "grey20"),
            panel.grid.minor = element_blank(),
            axis.text = element_text(size = 12),
            axis.ticks=element_blank())+
    facet_grid(Day~FUDR)
# ggsave("Bargraphs_Speed_700-890_s_d0-d4.pdf",width = 5, height = 7, dpi=300)

# ggsave("Day0_mean_speed_900_901s_OP50.pdf", width=5, height=5, dpi=600)
```

8) Calculate p-values using means of trackers: 
```{r}
ds <- MeanSpeed_800_890_s_per_Plate

t.test(ds[ds$Day=="1"&ds$Strain=="N2E"&ds$FUDR=="without","Speed"], 
    ds[ds$Day=="1"&ds$Strain=="e1370"&ds$FUDR=="without","Speed"])
```

